% ===========================
% Appendix C: AI-Based Recognition of Regularity via PH and Ext Collapse
% ===========================

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm,amsfonts,geometry,hyperref,listings,graphicx}
\geometry{margin=1in}
\title{Appendix C: AI-Based Recognition of Regularity via PH and Ext Collapse\\
\large Augmentation Strategy for Navier--Stokes Global Regularity Proof}
\author{A. Kobayashi \\ ChatGPT Research Partner}
\date{June 2025}

\begin{document}

\maketitle

\section*{Motivation}
This appendix outlines how recent upgrades in the \textbf{AK High-Dimensional Projection Structural Theory (v5.0)} can enhance the interpretation, detection, and numerical validation of global regularity for the 3D incompressible Navier--Stokes equations. 
We frame a bridge from \emph{topological collapse} and \emph{derived categorical degeneration} to \emph{AI-based recognition systems}.

\section*{C.1 Persistent Barcode Embedding and Detection}
We consider a family of velocity fields $\{u(t)\}$ evolving under NSE. Applying Isomap to the snapshots followed by persistent homology yields barcodes $\mathrm{PH}_1(u(t))$. These barcodes are then embedded as feature vectors:
\[ 
\mathrm{PH}_1(u(t)) \mapsto \mathbf{v}_t \in \mathbb{R}^d
\]
using geometric or neural encoders. This allows classification of topological collapse patterns indicative of smoothness.

\section*{C.2 Spectral Collapse as Ext-Degeneration}
Dyadic shell energies $E_j(t)$ are computed as:
\[ 
E_j(t) = \sum_{k \in \text{Shell}_j} |\hat{u}_k(t)|^2
\]
and interpreted as Ext-degeneration signatures:
\[
\forall j,\ E_j(t) \downarrow 0 \ \Longleftrightarrow\ \mathrm{Ext}^1(F_t, -) \to 0
\]
where $F_t \in D^b(\mathcal{AK})$ models the derived categorical state. 
This collapse aligns with AK-HDPST's notion of \textit{derived-finality}.

\section*{C.3 Learning Degeneration Phases via AI}
Construct a training set labeled by smooth/singular evolution and feed it into a classifier over:
\[ 
(\mathbf{v}_t,\ \vec{E}(t),\ \text{Isomap}(u(t))) \in \mathbb{R}^{d+m+n} 
\]
where $\vec{E}(t)$ encodes dyadic shells. 
Supervised models (e.g., SVMs, neural nets) learn to recognize regularity patterns from topological and spectral cues.

\section*{C.4 Summary and GitHub Integration}
This AI-augmented perspective allows us to numerically monitor regularity, quantify topological triviality, and validate theoretical predictions in AK-HDPST. This module is designed to accompany:
\begin{itemize}
  \item \textbf{Main Repository:} \url{https://github.com/Kobayashi2501/Navier-Stokes-Global-Regularity}
  \item \textbf{AK-HDPST v5.0:} \url{https://github.com/Kobayashi2501/AK-High-Dimensional-Projection-Structural-Theory}
\end{itemize}

\end{document}
